---
title: "R Notebook"
output: html_notebook
---
Research Question: Do movies from the 2000s with a higher budget also have a higher revenue?

Variables:
* Movie Title
* Date
* Year
* Budget
* Revenue

Geometric shape required: 
* Scatterplot Graph
```{r}
#Load Data
library(tidyverse)
movies <- read_csv('movies.csv')
```
Here I filter only the movies from the 2000s with budget and revenue > 0.  
```{r}
movies_2000s <- movies %>%
  filter(decade=='2000s') %>%
  filter(budget > 0) %>%
  filter(revenue > 0)
```
Here I plot the relationship between budget vs. revenue for movies produced in the 2000s.
```{r}
ggplot(data = movies_2000s) +
  geom_point(mapping = aes(x = budget, y = revenue,)) +
  xlab("budget ($)")+
  ylab("revenue ($)") +
ggtitle("Revenue vs Budget for 2000s Movies")
```
A general trend that we see is that movies produced generate a revnenue that is similarly around their budget expenditure. 

---
title: "Arne Exercise2"
output: html_notebook
Introduction - same as exercise 1
```{r}
#Load Data
library(tidyverse)
movies <- read_csv('movies.csv')
```
Here I filter only the movies from the 2000s that budget and revenue > 0.  
```{r}
movies_2000s <- movies %>%
  filter(decade=='2000s') %>%
  filter(budget > 0) %>%
  filter(revenue > 0)
```
Here I group movies by their average rating whether > 7 or <= 7. 
```{r}
movies_2000sratings <- movies_2000s %>%
mutate(
  movie_ratingover7 = ifelse(vote_average > 7, "over 7", "lower than 7")
  )
```

```{r}
ggplot(data = movies_2000sratings) +
  geom_point(mapping = aes(x = budget, y = revenue, color = movie_ratingover7))+
  xlab("budget ($)")+
  ylab("revenue ($)") +
ggtitle("Revenue vs Budget for 2000s Movies")
```
It looks like there is a greater amount of movies with ratings lower than 7 than over 7. 
Movies with ratings lower than 7 in general, seem to also have lower budgets than their counterpart. 
